\chapter{Maintaining and Servicing the PR2}

The PR2 hardware requires little maintenance, but from time to time, you may be expected to service or perform minor repairs on your PR2. The information in this section will point you to the correct resources for hardware maintenance and servicing.

If you have any questions about a PR2 hardware problem, or contact PR2 Support.

\section{Regular Maintenance}

\subsection{Software and Upgrades}

For software upgrades of the PR2 and the basestation, please see the chapter on the PR2 computers.

\subsection{Hardware Maintenance}

Generally, your PR2 will require very little hardware maintenance. The procedures listed below are the only type of preventative maintenance that users should be doing. 

All hardware maintenance instructions and procedures are available in the \href{http://pr2support.willowgarage.com/wiki/PR2 Service Information}{PR2 Service Information} section of the PR2 Support site. 

\subsubsection{Fan Filter Cleaning / Replacement}

From time to time, you may have to clean the fan filter on your PR2. Generally, you will know when it is time to clean the fan filter of the robot if the main fan becomes very loud. Instructions for cleaning and replacing the fan filter are available under \href{http://pr2support.willowgarage.com/wiki/PR2 Service Information}{PR2 Service Information} on the PR2 Support website.

\subsubsection{Counterbalance Adjustment}

The PR2 arms use a counterbalance mechanism to adjust for the weight of the arm. Over time, this counterbalance may loosen, or you may wish to adjust the counterbalance as part of a modification of the arm. The \href{http://pr2support.willowgarage.com/wiki/PR2 Service Information}{PR2 Service Information} page provides a guide to adjusting the PR2 arm counterbalance.

\section{Hardware Problems and Diagnosis}

If you have any hardware, electrical or computer problems with your PR2, you can use the PR2 Diagnostics and PR2 Support resources to diagnose and fix it.

\subsection{Diagnostics System}

The first step if you suspect hardware problems should be to check the diagnostics display in pr2\_dashboard. If you find any errors in the diagnostics system, check the \href{http://pr2support.willowgarage.com/wiki/FAQ}{FAQ} to see if it relates to a known problem.

\subsection{PR2 Systemcheck}

The \texttt{pr2-systemcheck} utility can perform a short self-test of the PR2. 

To run pr2-systemcheck, run \texttt{robot stop} to shut down ROS software. (For robots running Ubuntu Jaunty, run \texttt{sudo robot stop}). Then run \texttt{sudo pr2-systemcheck}. 

If you find any errors on the from \texttt{pr2-systemcheck}, check the \href{http://pr2support.willowgarage.com/wiki/FAQ}{FAQ} to see if it relates to a known problem.

\section{Support}

PR2 Support is available from mailing lists, the PR2 Support site, or from tickets to Willow Garage. Support from mailing lists and the PR2 Support site is free and available to anyone. Tickets to Willow Garage support are not free. Check your PR2 purchase agreement or Beta Program Agreement for details on service charges.

\subsection{Mailing Lists and Software Documentation}

Please see ``Writing Code on the PR2'' for a complete list of mailing lists and Trac system for software problems.

\subsection{Report a Hardware Problem}

For hardware issues, please submit a ticket at \href{http://pr2support.willowgarage.com}{PR2 Support}. The Willow Garage engineering team will assist in diagnosing and fixing your problem.

\section{Additional Documentation}

Complete documentation on the PR2 modularity specifications, remove and replace instructions and other maintenance procedures is available at \href{http://pr2support.willowgarage.com}{PR2 Support}.

\subsection{FAQ}

The \href{http://pr2support.willowgarage.com/wiki/FAQ}{FAQ} in the PR2 Support website lists a number of common problems and fixes to your PR2. The FAQ is written by members of the Willow Garage engineering team. Please check the FAQ before filing a hardware ticket.

\subsection{Software Documentation}

The \href{http://www.ros.org/wiki}{ROS Wiki} contains all documentation for ROS and related software.

\subsection{PR2 Modularity Specifications}

The PR2 Modularity Specification is available on the PR2 Support website under \href{http://pr2support.willowgarage.com/wiki/PR2 Modularity}{PR2 Modularity}. The modularity specifications cover mechanical and electrical interfaces to key PR2 components.

\subsection{PR2 Remove/Replace Instructions}

The PR2 Support website contains instructional documents for removing and replacing sub-assemblies of the PR2 under \href{http://pr2support.willowgarage.com/wiki/PR2 Service Information}{PR2 Service Information}.
